Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
nouns to verbs

Group fluxes are shown in \Cref{fig:group1,fig:group2}. The effect of the vacuum
boundary conditions is shown clearly in the cosinusoidal shapes in radial and
axial directions. Striations are observed in both fast and thermal fluxes, with
the fast group preferring the fuel and the thermal group preferring the moderator.

@@

\Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
profiles with cosinusoidal gamma heating and \gls{MSRE} design models
\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. The
profiles are in good agreement. In the \gls{MSRE} design, the moderator
temperature at the reactor inlet is about 20 degrees Faerenheit larger than the
fuel temperature, whereas the temperatures are about the same in the Moltres
model. This difference can perhaps be attributed to the neglection of axial
conduction in the \gls{MSRE} design model \cite[p. 99]{briggs_molten-salt_1964}.

>>>>

Group fluxes are shown in \Cref{fig:group1,fig:group2}. The effect of the vacuum
boundary conditions is shown clearly in the cosinusoidal shapes in radial and
axial directions. Both the fast and thermal fluxes are striated, with
the fast group preferring the fuel and the thermal group preferring the moderator.

@@

\Cref{fig:temp_compare} shows a comparison between Moltres predicted temperature
profiles with cosinusoidal gamma heating and \gls{MSRE} design models
\cite{briggs_molten-salt_1964} in the hottest channel and adjacent graphite. The
profiles are in good agreement. In the \gls{MSRE} design, the moderator
temperature at the reactor inlet is about 20 degrees Faerenheit larger than the
fuel temperature, whereas the temperatures are about the same in the Moltres
model. This difference is likely because axial
conduction was neglected in the \gls{MSRE} design model \cite[p. 99]{briggs_molten-salt_1964}.
